### 2013-06-13 Tex/chapters/model.tex
Subfigure: Unterbilder werden nummeriert und im lof angezeigt

    To construct these graphs the simple way is to test for every
    pair of nodes for every node if it lies in the lune of the pair.
    That is of complexity \(O (n^3)\).\\
    To reduce the complexity one can first create a Delaunay
    Triangulation in complexity \(O (n \log n)\)
    \cite{Leach1992} and test the criterion for each edge, because
    the Delaunay Triangulation is a supergraph of both. But the
    implementation of a Delaunay Triangulation algorithm is not
    trivial and the generation of the graphs is not time critical in
    the scope of this bachelor thesis.\\
    So a tradeoff is to use basicly the simple method but only test
    the criterion for nodes which are near to the lune and abort if
    one node inside the lune is found. To determine which nodes are
    near the lune one can subdivide the area in \emph{cells} and save
    for each cell a list with nodes lying inside it \cite{RNGCell}.
    Now it is just neccessary to test the nodes in the cells which
    resemble a rectangular bounding box of the lune. Most pairs will be
    far away from each other and the cells in the middle of the bounding
    box are completely inside the lune so that only one node has to be
    tested to discard an edge between them. Connected nodes are near to
    each other so that only very few cells have to be tested.\\
    Indeed this method reduced the time needed to construct a Relative
    Neighborhood graph with \(N=32^2\) and \(N=64^2\) by a factor of
    over \(15\) respectivly \(40\). But no further analysis was made.

>>>>

    To construct these graphs the simple way is to test for every
    pair of nodes for every node if it lies in the lune of the pair.
    That is of complexity \(O (n^3)\).\\
    To reduce the complexity one can first create a Delaunay
    Triangulation in complexity \(O (n \log n)\)
    \cite{Leach1992} and test the criterion for each edge, because
    the Delaunay Triangulation is a supergraph of both. But the
    implementation of a Delaunay Triangulation algorithm is not
    trivial and the generation of the graphs is not time critical in
    the scope of this bachelor thesis.\\
    So a tradeoff is to use basicly the simple method but only test
    the criterion for nodes which are near to the lune and abort if
    one node inside the lune is found. To determine which nodes are
    near the lune one can save the position of every node in a
    \emph{cell list} according to \cite{RNGCell} and just test the
    nodes in the cells which resemble a rectangular bounding box of the
    lune.
